---
title: "flexdashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(viridis)
library(plotly)
library(stringr)
library(forcats)
library(tidytext) 
library(ggridges)
library(ggplot2)
```

```{r dataimput, include=FALSE}
library(tidyverse)
library(httr)
library(jsonlite)

get_all_inspections = function(url) {
  
  all_inspections = vector("list", length = 0)
  
  loop_index = 1
  chunk_size = 50000
  DO_NEXT = TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] = 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
                       )
          ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT = dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index = loop_index + 1
  }
  
  all_inspections
  
}

url = "https://data.cityofnewyork.us/resource/9w7m-hzhe.json"

nyc_inspections = get_all_inspections(url) %>%
  bind_rows() 
```
```

Column {data-width=650}
-----------------------------------------------------------------------

### Density Plot of Score vs Top 5 Kinds of Cuisine 

```{r}
top_5_cuisine = nyc_inspections %>%
  select(score, cuisine_description) %>%
  drop_na() %>%
  count(cuisine_description, sort = TRUE) %>%
  top_n(5) %>%
  select(cuisine_description)

cuisine_density = nyc_inspections %>%
  inner_join(., top_5_cuisine) %>%
  select(score, cuisine_description) %>%
  mutate(score=as.numeric(score))%>%
  ggplot(aes(score, fill = cuisine_description)) + 
  geom_density(alpha = 0.2)
  
ggplotly(cuisine_density)
```


Column {data-width=350}
-----------------------------------------------------------------------

### Boxplot of Score vs Boro

```{r}
nyc_inspections %>%
  filter(!boro == "Missing") %>%
  mutate(score = as.numeric(score),
         boro = as.factor(boro),
         boro = fct_reorder(boro, score)) %>% 
  plot_ly(y = ~score, color = ~boro, type = "box",
          colors = "Set2")
```

### Top 10 Words Appearing in Inspections

```{r}
inspection_words = nyc_inspections %>%
  filter(grade %in% c("A", "B", "C")) %>%
  mutate(inspection_num = row_number(),
         boro = str_to_title(boro)) %>% 
  select(inspection_num, boro, grade, score, critical_flag, dba, cuisine_description, zipcode, violation_description)%>% 
  unnest_tokens(word, violation_description) %>%
  anti_join(stop_words)

inspection_words %>%
  count(word, sort = TRUE) %>%
  top_n(10) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  plot_ly(x =~ word, y = ~n, color =~ word, type = "bar", colors = "Set1")

```

